---
author: Jared P. Lander
title: Markdown Primer
date: The Day After Halloween with no Candy
output: html_document
---

```{r setup,echo=FALSE}
knitr::opts_chunk$set(cache=TRUE,echo=TRUE)
```


# My First Section

This is a paragraph in my first section. Anything on the same line, even if it wraps around in the editor, is part of the same paragraph. Adding a third sentence to comply with antiquated rules of grammar.

To start a new paragraph, leave a blank line after the previous paragraph. Just like Mark Twain, we'll show disdain for old rules, and skip the third sentence.

# Another Section

Start a new section with a single hashtag. No need to close the previous section, just like in LaTeX. Super simple is a sentence fragment.

# Subsections

We started a third section with a single hashtag. Within this section we'll create subsections.

## First Subsection

We started a subsection, within the previous section, with two hashtags. And this line becomes a paragraph in that subsection.

# Lists

## Unordered Lists

- Root
- Ginger
- Birch

## Ordered List

1. New York
    - Coal
    - Gas
    - Wood
1. New Jersey
    - Gas
1. Rome
    - Wood
1. Naples
1. Philadelphia
1. Detroit

# Text Formatting

_this text will be emphasized_

__this text will be strong__

___this text will be emphasized and strong___

`this will look like code or an old-timey typewriter`

# Links

[My website](http://www.jaredlander.com)

# R Time!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!

```{r}
1 + 1
```


```{r}
x <- 2
x
```

```{r}
x*4
```

```{r more-math,cache=TRUE}
17 + 2
```

# Plots

```{r diamonds-scatter,echo=FALSE,cache=TRUE,dependson='more-math',fig.align='center',fig.cap='Scatterplot of diamond price vs size and cut',}
library(ggplot2)
ggplot(diamonds, aes(x=carat, y=price, color=cut)) + geom_point()
```
